### 2015-06-30 text/ms.Rmd
Edit the whole paper

There are often multiple models we can apply to an ecological system to assess
population status and trajectory. Models might incorporate different data
types, assume alternate population dynamics, or make contrasting assumptions
about the starting state of a system. These models may suggest different
conclusions about population status and trajectory and we often do not know
which model is best. How can we reconcile multiple models to make robust
management decisions about ecological resources?

Ensemble methods, which combine the output from multiple models as predictors
in a new 'ensemble' model, are one solution to this problem. A simple ensemble
model might take the average of multiple model outputs, perhaps weighted by
some goodness of fit. A complex ensemble model might also take into account
non-linear interactions between model outputs and additional covariates.
Ensemble models are popular in other fields including public health
[@thomson2006], agriculture [@cantelaube2005], climate science [@murphy2004;
@tebaldi2007; @pierce2009], and machine learning [@dietterich2000]. We think
they have tremendous opportunity in ecological resource management.

@@

We tested the ability of ensemble models to improve estimates of population
status and trajectory when applied to both a large simulated dataset and a
global database of assessed stock status. Here we describe the datasets,
individual models of population status, and ensemble methods to combine those
estimates. We then describe how we evaluated the ability of the various models
to estimate population status.

## Datasets

We first developed and tested ensemble models with a fully factorial simulated
dataset [@rosenberg2014]. In summary, the simulation models included three life
histories: small pelagic, demersal, large pelagic; three levels of how depleted
biomass was at the start of the dataset compared to carrying capacity: 100%,
70%, and 40% of carrying capacity; and four exploitation dynamics: a constant
exploitation rate, a exploitation rate that is coupled with biomass to mimic an
open-access single-species fishery, a scenario where exploitation rate
increases to a fixed level, and a 'roller-coaster' scenario where the
exploitation rate increases and then decreases. Process noise was introduced to
the models through two levels of multiplicative recruitment variability: $N(0,
0.2)$ and $N(0, 0.6)$, and that process noise was either uncorrelated or had a
first-order autoregressive correlation of 0.6. The simulation included a
scenario without observation error and with multiplicative observation error
around catch at $N(0, 0.2)$.

Rosenberg et al. [@rosenberg2014] ran ten iterations for each combination of
factors adding stochastic draws of recruitment and catch-recording variability
each time to generate a total of 5760 stocks. The simulation models were built
in the package `FLR` [@kell2007] for the statistical software \textsf{R}
[@r2015]. The simulation model and the code to generate the simulations is
available at <https://github.com/flr/StockSims> (TODO: not there).

We also tested our ensemble models on the RAM Legacy Stock Assessment Database
[@ricard2012]. Our analysis of the stock-assessment database was based on
version XX downloaded on XX. After removing stocks for which the models
described below did not converge, this database included `r ram_stocks_n` from
XX countries.

@@

\noindent
where $\hat{B}_{t+1}$ represents predicted biomass at time $t$ plus one year,
$B_t$ represents biomass at time $t$, $r$ represents the intrinsic population
growth rate, $B_0$ represents unfished biomass or carrying capacity, and $C$
represents catch. @rosenberg2014 provide a full summary of these four methods
and code to fit all the models is available in an accompanying package
`datalimited` for the statistical software \textsf{R}. In summary:

* *COM-SIR* (catch-only-model with sample-importance-resampling) is a coupled
  harvest-dynamics model @vasconcellos2005. Biomass is assumed to follow a
  Schaefer model and harvest dynamics are assumed to follow a logistic model.
  The model is fit with a sample-importance-sampling algorithm developed in
  @rosenberg2014.

@@

* *mPRM* (modified panel regression model) is a modified version of the
  panel-regression model from Costello et al. [@costello2012]. Unlike the other
  models considered, mPRM is empirical and not mechanistic---it uses the RAM
  Legacy Stock Assessment database to fit a linear model to a series of
  characteristics of the catch time series and stock with stock-assessed
  \bbmsy\\ as the response. The model used in this paper and @rosenberg2014 is
  modified from the original in that it condenses the life-history categories
  into three categories to match the simulated dataset, removes the maximum
  catch predictor since the absolute catch in the simulated dataset is
  arbitrary, and does not implement the bias correction needed in Costello et
  al. [@costello2012] for deriving aggregate estimates of mean status across
  multiple stocks. (*TODO: can we avoid listing most of these modifications or
  relegate them to the supplement?*)

@@

Ensemble methods allow us to incorporate additional covariates into our models
and potentially leverage interactions between these covariates and individual
model predictions. Additional covariates could be, for example, life-history
characteristics, information on exploitation patterns, or statistical
properties of the data. For simplicity, and to allow us to apply models
developed with the simulated dataset to the real-world dataset, we added one
set of additional covariates: spectral properties of the catch time series.
Spectral analysis decomposes a time series into the frequency domain and
provides a means of describing the statistical properties of the catch series
that is independent of time series length and magnitude of catch. We fit
spectral models to the scaled catch time series (catch divided by maximum
catch) with the `spec.ar` function in \textsf{R} and recorded representative
short- and long-term spectral densities at frequencies of 0.20 and 0.05, which
correspond to 5- and 20-year cycles.

@@

An ensemble model can combine models through anything from a simple average to
a complex non-linear model. Here we chose four ensemble models to compare: an
average, a linear model with two-way interactions, a random forest, and boosted
regression tree. The general form of our models was

@@

\noindent 
where $L$ is a generalized loss function, $f$ is some generalized regression
function, $\hat{b}_\mathrm{CMSY}$ is the mean or slope prediction from the CMSY
model etc. (Table \ref{tab:predictors}), $S(0.2)$ and $S(0.05)$ represent the
spectral density of the scaled catch series at frequencies of 0.2 and 0.05, $b$
is the mean or slope value the model is fitted to, and $\theta$ is the set of
parameters for the regression function. For all ensemble models of mean
\bbmsy\\, which is bounded at zero, we fit the models in log space and
exponentiated the predictions to derive a median estimate of \bbmsy\\. For the
estimates of \bbmsy\\ slope, we fit ensemble models on the natural
untransformed scale.

We calculated the average ensemble models as the geometric mean of the
individual model \bbmsy\\ estimates and the mean of the individual model
\bbmsy\\ slopes. We fit the linear model ensemble with second-order
interactions. We fit two machine learning ensemble models based on regression
trees. Regression trees sequentially determine what value of a predictor best
splits the response data into two 'branches' based on a specified loss
function. In random forests, a series of regression trees are built on a random
subset of the data and random subset of the covariates of the model (REF). In
generalized boosted models (GBMs), each subsequent model is fit to the
residuals from the previous model; data points that are fit poorly in a given
model are given more weight in the next model [@elith2008]. Random forests and
GBMs can provide strong predictive performance and fit highly non-linear
relationships [@elith2008; @hastie2009]. We fit random forest models with the
`randomForest` package [@liaw2002] for \textsf{R} with the default argument
values. We fit boosted regression tree models with the `gbm` package
[@ridgeway2015] for \textsf{R}. Based on cross-validation with the **caret**
\textsf{R} package, we fit GBMs with 2000 trees, an interaction depth of $6$, a
learning rate (shrinkage parameter) of $0.01$, and all other arguments at their
default values.

@@

Predictive performance can be evaluated with metrics that represent a variety
of modelling goals. For continuous response variables such as the mean and
slope of population status, performance metrics often measure some form of
bias, precision, accuracy (a combination of bias and precision), or the ability
to correctly rank or correlate across populations (REFs). Here, we measure
proportional error (PE; also called 'relative error') defined as $(\hat{b} -
b)/b$. We summarize median proportional error to measure bias, median absolute
proportional error to measure accuracy, and Spearman's rank-order correlation
to measure the ability to correctly rank populations.

@@

Applied to the simulated dataset of known status, the individual models had
variable success at recovering the mean (status) and slope (trajectory) of
\bbmsy\\ in the last five years. All models exhibited a high degree of scatter
around the 1:1 line of perfect status prediction (Fig. \ref{hexagon}). CMSY
exhibited bimodal predictions of status but had the best rank-order correlation
and accuracy scores (Fig. \ref{performance}a). COM-SIR and SSCOM both correctly
identified a number of low status stocks, but frequently predicted a high
status when status was in fact low (Fig. \ref{hexagon}b, c). mPRM had
relatively poor ability to predict status for the simulated dataset (Fig.
\ref{hexagon}d). There was generally little correlation between true and
predicted trajectory for any of the individual models besides SSCOM (Figs
\ref{scatter-sim-slope}a--d, \ref{performance-sim-slope}).

Ensemble models, and in particular the machine learning ensemble models (random
forest and GBM), generally improved estimates of status and trajectory (Fig.
\ref{hexagon}e--h, Fig. \ref{scatter-sim-slope}e--h). Compared to the
individual models, machine learning ensembles improved accuracy (median
absolute proportional error) by 
`r mean_sim$mach_vs_ind_mare_fold`%, 
increased rank-order correlation from `r mean_sim$ind_corr_range` 
to `r mean_sim$mach_corr_range`, 
and reduced bias (median proportional error) from 
`r mean_sim$ind_mre_range` to 
`r mean_sim$mach_mre_range` (Fig. \ref{performance}a). 
These ensembles also had better ability to distinguish if
simulated stocks were above or below $B/B_\mathrm{MSY} = 1$ (Fig.
\ref{roc-sim}). Results were similar when predicting trajectory: compared to
individual models, machine learning ensembles improved accuracy by 
`r slope_sim$mach_vs_ind_mare_fold`%, increased rank-order correlation from 
`r slope_sim$ind_corr_range` to 
`r slope_sim$mach_corr_range`, and reduced bias
from `r slope_sim$ind_mre_range` 
to `r slope_sim$mach_mre_range` (Fig. \ref{performance-sim-slope}). The
ensemble models that simply took a mean of the individual models ranked
slightly behind the best individual model for estimating status (CMSY; Fig.
\ref{performance}a) and had slightly lower correlation but higher accuracy than
the best individual model at predicting slope (SSCOM; Fig.
\ref{performance-sim-slope}).

The ensemble models were able to improve the predictions of status by
exploiting the best properties of individual models, the covariance between
individual models, and interactions with other covariates. For example, SSCOM
had strong predictive ability when it predicted low \bbmsy\\ (Fig.
\ref{hexagon}c, Fig. \ref{partial-sim}c) and CMSY predictions were
approximately linearly related to \bbmsy\\ within the low and high prediction
clusters (Fig. \ref{partial-sim}). Ensembles also exploited the covariance
between individual model predictions. For instance, both the linear model and
GBM ensemble suggest that if mPRM and SSCOM predict high status, the true
status also tends to be high (Figs \ref{lm-coefs}, \ref{partial-2d-sim}l). The
addition of spectral density covariates helped the ensemble models correctly
predict higher status values (Fig. \ref{hexagon}g, h) by exploiting
interactions between the spectral density predictors and the individual model
predictions (Fig. \ref{partial-2d-sim}). Although the additional covariates
improved ensemble fit, performance of the ensembles was only marginally
degraded by removing these covariates (Fig. \ref{hexagon} vs. Fig.
\ref{hexagon-sim-basic}) TODO NEW FIG THAT QUANTIFIES THIS.

When applied to the stock assessment database, the ensemble models---trained
exclusively on the simulated dataset---generally performed as well or better
than the best individual models. The mean, random forest, and GBM ensembles
even outperformed the mPRM method which is trained on the RAM Legacy Stock
Assessment database itself (Fig. \ref{performance}b, Fig. \ref{hexagon-ram}).
Compared to the individual models, the machine learning ensembles increased
accuracy by `r mean_ram$mach_vs_ind_mare_fold`%, 
improved correlation from `r mean_ram$ind_corr_range` to 
`r mean_ram$mach_corr_range`, and reduced bias from
`r mean_ram$ind_mre_range` to `r mean_ram$mach_mre_range`.

@@

Ensemble methods provide a useful approach to situations where conservation and
management decisions must be made on the basis of multiple, potentially
contrasting estimates of status---a situation common to many ecological
settings beyond fisheries. Compared to individual models of fish population
status, ensemble models were consistently the best or among the best across
three performance dimensions, two response variables, two datasets, and
multiple ensemble model types. Our results suggest choosing an ensemble model
that allows for non-parametric relationships, such as machine learning
methods---these methods provide added insight into individual model behaviour
and generally performed the best---but even a simple average of predictions
across multiple models may be useful.

@@

Multi-model inference in the form of coefficient averaging weighted by
information theoretics such as the Akaike Information Criteron (AIC) is a
common analytical approach in ecology [@burnham2002; @grueber2011]. The
ensemble methods described in this paper share similarities with coefficient
averaging but differ in other important ways. Ensemble models and coefficient
averaging share the long-held notion that multiple working hypotheses can
contribute useful information for inference [@chamberlin1890]. A fundamental
difference is that coefficient averaging focuses on a averaging *coefficients*
whereas ensembles instead average *predictions*. By focussing on predictions,
ensembles do not suffer from the muddled inference of coefficient averaging
when coefficients covary [@cade2015] and are a more general purpose tool: they
do not require information theoretics, they can combine different types of
models (e.g. parametric and non-parametric models or frequentist and
Bayesian predictions), and they can combine predictions in complex non-linear
ways that may depend on additional covariates.

A strength of ensemble models is that they can be tailored or specific response
variables. For example, we built separate ensemble models of mean \bbmsy\\ and
the slope of \bbmsy\\. The same set of model weights or non-linear
relationships need not hold across different response variables. For example,
SSCOM contributed little to the GBM ensemble estimate of status at higher
levels of predicted \bbmsy\\, but contributed strongly to estimates of slope
(TODO FIG). Formally, this fitting of ensemble models to specific quantities of
interest provides an additional calibration step [@rykiel1996]. Individual
models are typically calibrated (i.e. parameters are estimated) based on a
single response variable; however, this model might then provide a biased or
inaccurate estimate of quantities. For example, a data-limited fisheries model
might calibrate parameters by maximizing likelihood with respect to observed
and predicted catches but those parameters may then provide a biased or
inaccurate estimate of the mean and slope of \bbmsy\\. Ensemble methods can
provide a final calibration step to a quantity of interest.

@@

Combining predictions from multiple models via ensemble methods is also broadly
useful in other subfields of ecology and fisheries science. Predictions about
extinction risk are widely used at the national (e.g. the US Endangered Species
Act and the Canadian Species at Risk Act) and international (e.g. the IUCN Red
List, [@iucn2015]) levels. These risk assessments generally involve fitting
regression models to outcomes for individual species along with predictors of
species risk (e.g. [@anderson2011a; @pinsky2011)], or population dynamics models
to data for individual species (e.g. [@dfo2010]). Both types of models are prone
to error caused by model-misspecification and therefore results are sensitive
to decisions about model structure [@brooks2015]. Although there are options to
account for potential model-misspecification in determination of species risk
(e.g., coefficient averaging, [@burnham2002], or semi-parametric methods,
[@thorson2014]), ensemble methods are a relatively simple way to combine
predictions in a transparent manner. Beyond estimates of status and trajectory,
ensemble methods could be used to increase the robustness of spatial
predictions when designing networks of protected areas [@rassweiler2014], or to
forecast potential spatial shifts in species distribution given climate impacts
[@harsch2014].

>>>>

There are often multiple models we can apply to an ecological system
[@hilborn1997; @burnham2002]. Models might incorporate different data types,
assume alternate population dynamics, or make contrasting assumptions about the
starting state of a system. These models may suggest different conclusions
about population status and trajectory and we often do not know which model is
best. How can we reconcile multiple models to make robust management decisions
about ecological resources?

Ensemble methods, which combine the output from multiple models as predictors
in a new 'ensemble' model, are one possible solution to this problem. A simple
ensemble model might take the average of multiple model predictions, perhaps
weighted by some goodness of fit. A complex ensemble model might also take into
account non-linear interactions between model predictions and additional
covariates. Ensemble models are popular in other fields including public health
[@thomson2006], agriculture [@cantelaube2005], climate science [@murphy2004;
@tebaldi2007; @pierce2009], and machine learning [@dietterich2000]. 
<!--We think they have tremendous opportunity in ecological resource management.-->

@@

<!--
We tested the ability of ensemble models to improve estimates of population
status and trajectory when applied to both a large simulated dataset and a
global database of assessed stock status. Here we describe the datasets,
individual models of population status, and ensemble methods to combine those
estimates. We then describe how we evaluated the ability of the various models
to estimate population status.
-->

<!--
## Datasets
-->

We first developed and tested ensemble models with a fully factorial simulated
dataset [@rosenberg2014]. These previously published simulation models included
three life histories: small pelagic, demersal, large pelagic; three levels of
how depleted biomass was at the start of the dataset compared to carrying
capacity: 100%, 70%, and 40% of carrying capacity; and four exploitation
dynamics: a constant exploitation rate, a exploitation rate that is coupled
with biomass to mimic an open-access single-species fishery, a scenario where
exploitation rate increases to a fixed level, and a 'roller-coaster' scenario
where the exploitation rate increases and then decreases. Process noise was
introduced to the models through two levels of multiplicative recruitment
variability: $N(0, 0.2)$ and $N(0, 0.6)$, and that process noise was either
uncorrelated or had a first-order autoregressive correlation of 0.6. The
simulation included a scenario without observation error and with
multiplicative observation error around catch at $N(0, 0.2)$.

Rosenberg et al. [@rosenberg2014] ran ten iterations for each combination of
factors adding stochastic draws of recruitment and catch-recording variability
each time to generate a total of 5760 stocks. The simulation models were built
in the package `FLR` [@kell2007] for the statistical software \textsf{R}
[@r2015]. The code to generate the simulations is available at
<https://github.com/flr/StockSims> (TODO: not there).

We also tested our ensemble models on the RAM Legacy Stock Assessment Database
[@ricard2012]. Our analysis of the stock-assessment database was based on
version XX downloaded on XX. After removing stocks for which the models
described below did not converge, this database included `r ram_stocks_n`
stocks.

@@

\noindent
where $\hat{B}_{t+1}$ represents predicted biomass at time $t$ plus one year,
$B_t$ represents biomass at time $t$, $r$ represents the intrinsic population
growth rate, $B_0$ represents unfished biomass or carrying capacity, and $C$
represents catch. Rosenberg et al. [@rosenberg2014] provide a full summary of
these four methods and code to fit all the models is available in an
accompanying package `datalimited` for the statistical software \textsf{R}. In
summary:

* *COM-SIR* (catch-only-model with sample-importance-resampling) is a coupled
  harvest-dynamics model @vasconcellos2005. Biomass is assumed to follow a
  Schaefer model and harvest dynamics are assumed to follow a logistic model.
  The model is fit with a sample-importance-sampling algorithm [@rosenberg2014].

@@

* *mPRM* (modified panel regression model) is a modified version of the
  panel-regression model from Costello et al. [@costello2012]. Unlike the other
  models, mPRM is empirical and not mechanistic---it uses the RAM
  Legacy Stock Assessment database to fit a regression model to a series of
  characteristics of the catch time series and stock with stock-assessed
  \bbmsy\\ as the response. The model used in this paper is
  modified from the original in that it condenses the life-history categories
  into three categories to match the simulated dataset, removes the maximum
  catch predictor since the absolute catch in the simulated dataset is
  arbitrary, and does not implement the bias correction needed in Costello et
  al. [@costello2012] for deriving aggregate estimates of mean status across
  multiple stocks.

@@

Ensemble methods allow us to incorporate additional covariates 
and potentially leverage interactions between these covariates and individual
model predictions. Additional covariates could be, for example, life-history
characteristics, information on exploitation patterns, or statistical
properties of the data. For simplicity, and to allow us to apply models
developed with the simulated dataset to the real-world dataset, we added only one
set of additional covariates: spectral properties of the catch time series.
Spectral analysis decomposes a time series into the frequency domain and
provides a means of describing the statistical properties of the catch series
that is independent of time series length and absolute magnitude of catch. We fit
spectral models to the scaled catch time series (catch divided by maximum
catch) with the `spec.ar` function in \textsf{R} and recorded representative
short- and long-term spectral densities at frequencies of 0.20 and 0.05, which
correspond to 5- and 20-year cycles.

@@

Here we compare four ensemble models of varying complexity: an average, a
linear model with two-way interactions, a random forest, and boosted regression
tree. The general form of our models was

@@

\noindent 
where $L$ is a generalized loss function, $f$ is some generalized regression
function, $\hat{b}_\mathrm{CMSY}$ is the mean or slope prediction from the CMSY
model etc. (Table \ref{tab:predictors}), $S(0.2)$ and $S(0.05)$ represent the
spectral density of the scaled catch series at frequencies of 0.20 and 0.05, $b$
is the mean or slope value the model is fitted to, and $\theta$ is the set of
parameters for the regression function. For all ensemble models of mean
\bbmsy\\---a ratio bounded at zero---we fit the models in log space and
exponentiated the predictions. For the estimates of \bbmsy\\ slope, we fit
ensemble models on the natural untransformed scale.

We calculated the average ensemble models as the geometric mean of the
individual model \bbmsy\\ estimates and the mean of the individual model
\bbmsy\\ slopes. We fit the linear model ensemble with second-order
interactions. We fit two machine learning ensemble models based on regression
trees. Regression trees sequentially determine what value of a predictor best
splits the response data into two 'branches' based on a specified loss
function [@breiman1984]. In random forests, a series of regression trees are
built on a random subset of the data and random subset of the covariates of the
model [@breiman2001]. In generalized boosted models (GBMs), each subsequent
model is fit to the residuals from the previous model; data points that are fit
poorly in a given model are given more weight in the next model [@elith2008].
Random forests and GBMs can provide strong predictive performance and fit
highly non-linear relationships [@elith2008; @hastie2009]. We fit random forest
models with the `randomForest` package [@liaw2002] for \textsf{R} with the
default argument values. We fit boosted regression tree models with the `gbm`
package [@ridgeway2015] for \textsf{R}. Based on cross-validation with the
**caret** \textsf{R} package, we fit GBMs with 2000 trees, an interaction depth
of $6$, a learning rate (shrinkage parameter) of $0.01$, and all other
arguments at their default values.

@@

Predictive performance can be evaluated with metrics that represent a variety
of modelling goals. For continuous response variables such as the mean and
slope of population status, performance metrics often measure some form of
bias, precision, accuracy (a combination of bias and precision), or the ability
to correctly rank or correlate across populations (e.g. [@walther2005]). Here,
we measure proportional error, defined as
$(\hat{b} - b)/b$, where $\hat{b}$ and $b$ represent estimated and 'true'
(or stock-assessed) mean or slope of \bbmsy\\. We calculated median proportional
error to measure bias, median absolute proportional error to measure accuracy,
and Spearman's rank-order correlation to measure the ability to correctly rank
populations.

@@

Applied to the simulated dataset of known status, the individual models had
variable success at recovering the mean (status) and slope (trajectory) of
\bbmsy\\ in the last five years. All models exhibited a high degree of scatter
around the 1:1 line of perfect status prediction (Fig. \ref{hexagon}). CMSY
exhibited bimodal predictions of status but had the best rank-order correlation
and accuracy scores (Fig. \ref{performance}a). COM-SIR and SSCOM both correctly
identified a number of low status stocks, but frequently predicted a high
status when status was in fact low (Fig. \ref{hexagon}b, c). mPRM had
relatively poor ability to predict status for the simulated dataset (Fig.
\ref{hexagon}d). There was generally little correlation between true and
predicted trajectory for any of the individual models besides SSCOM (Figs
\ref{scatter-sim-slope}a--d).

Ensemble models, and in particular the machine learning ensemble models (random
forest and GBM), generally improved estimates of status and trajectory over any individual model (Fig.
\ref{hexagon}e--h, Fig. \ref{scatter-sim-slope}e--h). Compared to the
individual models, machine learning ensembles improved accuracy (median
absolute proportional error) by 
`r mean_sim$mach_vs_ind_mare_fold`%, 
increased rank-order correlation from `r mean_sim$ind_corr_range` 
to `r mean_sim$mach_corr_range`, 
and reduced bias (median proportional error) from 
`r mean_sim$ind_mre_range` to 
`r mean_sim$mach_mre_range` (Fig. \ref{performance}a). 
These ensembles also had better ability to distinguish if
simulated stocks were above or below $B/B_\mathrm{MSY} = 1$ (Fig.
\ref{roc-sim}). Results were similar when predicting trajectory: compared to
individual models, machine learning ensembles improved accuracy by 
`r slope_sim$mach_vs_ind_mare_fold`%, increased rank-order correlation from 
`r slope_sim$ind_corr_range` to 
`r slope_sim$mach_corr_range`, and reduced bias
from `r slope_sim$ind_mre_range` 
to `r slope_sim$mach_mre_range` (Fig. \ref{performance-sim-slope}). The
ensemble models that simply took a mean of the individual models ranked
slightly behind the best individual model for estimating status (CMSY; Fig.
\ref{performance}a) and had slightly lower correlation but higher accuracy than
the best individual model at predicting slope (SSCOM; Fig.
\ref{performance-sim-slope}).

The ensemble models were able to improve the predictions of status by
exploiting the best properties of individual models, the covariance between
individual models, and interactions with other covariates. For example, SSCOM
had strong predictive ability when it predicted low \bbmsy\\ (Fig.
\ref{hexagon}c, Fig. \ref{partial-sim}c) and CMSY predictions were
approximately linearly related to \bbmsy\\ within the low and high prediction
clusters (Fig. \ref{partial-sim}). Ensembles also exploited the covariance
between individual model predictions. For instance, both the linear model and
GBM ensemble suggest that if mPRM and SSCOM predict high status, the true
status also tends to be high (Figs \ref{lm-coefs}, \ref{partial-2d-sim}l). The
addition of spectral density covariates helped the ensemble models correctly
predict higher status values (Fig. \ref{hexagon}g, h) by exploiting
interactions between the spectral density predictors and the individual model
predictions (Fig. \ref{partial-2d-sim}). Although the additional covariates
improved ensemble fit, performance of the ensembles was only marginally
degraded by removing these covariates (Fig. \ref{hexagon} vs. Fig.
\ref{hexagon-sim-basic}).

When applied to the stock assessment database, the ensemble models---trained
exclusively on the simulated dataset---generally performed as well or better
than the best individual models. The mean, random forest, and GBM ensembles
even outperformed the mPRM method which is trained directly on the RAM Legacy Stock
Assessment database itself (Fig. \ref{performance}b, Fig. \ref{hexagon-ram}).
Compared to the individual models, the machine learning ensembles increased
accuracy by `r mean_ram$mach_vs_ind_mare_fold`%, 
improved correlation from `r mean_ram$ind_corr_range` to 
`r mean_ram$mach_corr_range`, and reduced bias from
`r mean_ram$ind_mre_range` to `r mean_ram$mach_mre_range`.

@@

Ensemble methods provide a useful approach to situations where conservation and
management decisions must be made on the basis of multiple, potentially
contrasting estimates of status---a situation common to many ecological
settings beyond fisheries. Compared to individual models of fish population
status, ensemble models were consistently the best or among the best across
three performance dimensions (accuracy, bias, and rank-order performance), two
response variables (status and trajectory), two datasets (simulated and global
fisheries), and multiple ensemble model types (from a simple average to machine
learning models). Our results suggest choosing an ensemble model that allows
for non-parametric relationships, such as machine learning methods---these
methods provide added insight into individual model behaviour and generally
performed the best---but even a simple average of predictions across multiple
models may be useful.

@@

Multi-model inference in the form of coefficient averaging weighted by
information theoretics such as the Akaike Information Criteron (AIC) is a
common analytical approach in ecology [@burnham2002; @johnson2004;
@grueber2011]. The ensemble methods described in this paper share similarities
with coefficient averaging but differ in other important ways. Ensemble models
and coefficient averaging share the long-held notion that multiple working
hypotheses can contribute useful information for inference [@chamberlin1890]. A
fundamental difference is that coefficient averaging focuses on a averaging
*coefficients* whereas ensembles instead average *predictions*. By focussing on
predictions, ensembles do not suffer from the muddled inference of coefficient
averaging when coefficients covary [@cade2015] and are a more general purpose
tool: they do not require information theoretics, they can combine different
types of models (e.g. parametric and non-parametric models or frequentist and
Bayesian predictions), and they can combine predictions in complex non-linear
ways that may depend on additional covariates.

A strength of ensemble models is that they can be tailored or specific response
variables. For example, we built separate ensemble models of mean \bbmsy\\ and
the slope of \bbmsy\\. The same set of model weights or non-linear
relationships need not hold across different response variables. For example,
SSCOM contributed little to the GBM ensemble estimate of status at higher
levels of predicted \bbmsy\\, but contributed strongly to estimates of slope
(TODO FIG). Formally, fitting ensemble models to specific quantities of
interest provides an additional calibration step [@rykiel1996]. Individual
models are typically calibrated (i.e. parameters are estimated) based on a
single response variable; however, this model might then provide a biased or
inaccurate estimate of other quantities of interest. For example, a
data-limited fisheries model might calibrate parameters by maximizing
likelihood with respect to observed and predicted catches but those parameters
may then provide a biased or inaccurate estimate of the mean and slope of
\bbmsy\\. Ensemble methods provide a final calibration step to a quantity of
interest. This ensemble calibration could further include a loss function
tailored to the goals of the model, say placing greater weight on accuracy at
low status levels than higher values.

@@

Combining predictions from multiple models via ensemble methods is also broadly
useful in other subfields of ecology and fisheries science. Predictions about
extinction risk are widely used at the national (e.g. the US Endangered Species
Act and the Canadian Species at Risk Act) and international (e.g. the IUCN Red
List, [@iucn2015]) levels. These risk assessments generally involve fitting
regression models to outcomes for individual species along with predictors of
species risk (e.g. [@anderson2011a; @pinsky2011)] (*TODO instead get references
from official national/international risk assessments?*), or population
dynamics models to data for individual species (e.g. [@dfo2010]). Both types of
models are prone to error caused by model-misspecification and therefore
results are sensitive to decisions about model structure [@brooks2015].
Although there are options to account for potential model-misspecification in
determination of species risk (e.g., coefficient averaging, [@burnham2002],
generalized modeling [@yeakel2011], or semi-parametric methods,
[@thorson2014]), ensemble methods are a relatively simple way to combine
predictions in a transparent manner. Beyond estimates of status and trajectory,
ensemble methods could be used to increase the robustness of spatial
predictions when designing networks of protected areas [@rassweiler2014], or to
forecast potential spatial shifts in species distribution given climate impacts
[@harsch2014].
